Software Ticket Quality

### 2017-10-16 proposal/mprop.tex
Added another paper

@@

>>>>

\textbf{Analysis of Software Cost Estimation}\cite{grimstad2006framework}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors are trying to show that poor estimation analysis techniques 
    in software projects will lead to wrong conclusions regarding cost 
    estimation accuracy. Moreover, they also propose a framework for 
    better analysis of software cost estimation error.
  \item \textbf{What was the method?}
    They approached a real-world company where they conducted analysis on
    their cost estimation techniques.
  \item \textbf{What did they learn?}
    They learned that regular, straight-forward types of cost estimation analysis
    techniques error lead them to wrong conclusions. 
  \item \textbf{Relevance to our work}: it showed us that we need to be careful
    when selecting techniques for cost estimation in our own research.
\end{itemize}

@@

\textbf{Recognizing Contextual Polarity}\cite{wilson2005recognizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The paper's main goal is to experiment with automatically distinguishing
    between contextual and prior polarity.
  \item \textbf{What was the method?}
  \item \textbf{What did they learn?}
  \item \textbf{Relevance to our work}:
\end{itemize}
